### 2014-10-12 writing/AAAI SSS '15/join.tex
Tweaks to stats reporting.

\paragraph{Results} 
We found that the NTN model worked best with 11-dimensional vector
representations for the 80 sets and a 90-dimensional feature vector
for the classifier, though the performance of the model was not highly
dependant on either dimensionality setting. 
This model was able to correctly label 99.4\% (94.3
macroaveraged F1) of the provably derivable test examples, and 95.4\%
(92.2 macro-F1) of the remaining test examples. The simpler NN worked
best with 11 and 75 dimensions, respectively, but was able to achieve
accuracies of only 89.0\% (80.7 macro-F1) and 62.5\% (40.7 macro-F1),
respectively. Training accuracy was 99.8\% for the NTN and 95.4\% for
the NN.

>>>>

\paragraph{Results} 
We found that the NTN model worked best with 11-dimensional vector
representations for the 80 sets and a 90-dimensional feature vector
for the classifier, though the performance of the model was not highly
dependant on either dimensionality setting. 
Averaging over five randomly generated datasets, the model was able to correctly label 98.1\% (standard error $0.67\%$) of the provably derivable test examples, and 87.7\%
($SE = 3.59\%$) of the remaining test examples. The simpler NN worked
best with 11 and 75 dimensions, respectively, but was able to achieve
accuracies of only 84.8\% ($SE = 0.84\%$) and 68.7\% ($SE = 1.58\%$),
respectively. Training accuracy was 99.8\% ($SE = 0.04\%$) for the NTN and 94.7\% ($SE= 0.89\%$) for
the NN.
